Parallel Level-Set Methods on Adaptive Tree-Based Grids

### 2016-02-18 paper/peer-reviews/response_letter.tex

\documentclass{scrlttr2}
\usepackage{color}

\begin{document} 
\begin{letter} {Editorial Office, \\ Journal of Computational
Physics} 
\setkomavar{subject}{Re: JCOMP-D-15-00846}

\opening{Dear Editor,} 
We would like to appreciate the invaluable comments made by the reviewers. We
have made adjustments to our article, titled `\textbf{Parallel level-set methods
on adaptive tree-based grids}', to address the issues raised by the reviewers as
detailed below.

\begin{itemize} 
\item \textbf{Reviewer \#1} \\ 
The first reviewer has suggested to include ``\textit{some basic library codes
in appendix, each matching its level set algorithm}''. Indeed it is important
for the scientific community to share knowledge and facilitate ways for
reproducing scientific work for others. In the case of computational science,
unfortunately, this is a daunting task that is not always possible.  Many
scientific codes are highly specialized and are often too technical to be fitted
into a paper.

@@

Our library is coded in `\texttt{C++}' (with a mix of little `\texttt{C}' code).
We have made adjustments to the to algorithms to make them easier to understand.
However, we believe it is best not to directly use a `\texttt{C++}' syntax to
keep the pseudo-code language-agnostic and accessible to all readers.

@@

\vspace{.5cm}

\item ``\textit{In Algorithm 2, what is the definition of “rank”? “owner’s
  rank”? “mpirank”? “st”?}''

There were multiple references to ``\textit{rank}'' in the pseudo-code that 
would have caused confusion. We have made things clear by explicitly referring 
to ``\textit{owners\_rank}'' and ``\textit{mpirank}''. Also in the previous
pseudo-code ``\textit{st}'' was meant to indicate ``\texttt{MPI\_STATUS}''. Again
we have reorganized the pseudo-code to make this point clearer. We have also
added more comments and text to the caption to explain things in more details.

### 2016-02-18 paper/tex/applications.tex
update enright figure with blue color, add number of iterations for reinitilization, add citations for XSEDE, stampede and comet
first revision submitted to JCP.

The implementation of the Stefan problem relies on the components described in the previous sections, and it is therefore a good synthesis of the performance of the various algorithms. We monitored the performance of the code over five time iterations, as presented in Algorithm \ref{alg:stefan}, for two different maximum resolutions. In both cases, the forest is built on a $20\times20\times20$ macro-mesh. The maximum tree resolution for the small test is 9, leading to approximately 7M grid points, and the maximum resolution for the large test is 11, corresponding to 105M grid points. The results are presented in figure \ref{fig:stefan_scaling}, where ``\verb|Solution_Extension|'' refers to extrapolation procedure (see Algorithm \ref{alg:stefan} step 5). As expected from the results obtained for each component in the previous sections, our implementation of the Stefan problem exhibits very satisfactory scaling (cf.\ Table \ref{tab:scaling_stefan}).

@@

\begin{figure}[ht!]
\begin{center}
\subfigure{
\includegraphics[width=.24\textwidth]{stefan/nb2_iter19.png}
\includegraphics[width=.24\textwidth]{stefan/nb2_iter39.png}
\includegraphics[width=.24\textwidth]{stefan/nb2_iter59.png}
\includegraphics[width=.24\textwidth]{stefan/nb2_iter79.png}
}
\subfigure{
\includegraphics[width=.24\textwidth]{stefan/nb5_iter19.png}
\includegraphics[width=.24\textwidth]{stefan/nb5_iter39.png}
\includegraphics[width=.24\textwidth]{stefan/nb5_iter59.png}
\includegraphics[width=.24\textwidth]{stefan/nb5_iter79.png}
}
\subfigure{
\includegraphics[width=.24\textwidth]{stefan/nb8_iter19.png}
\includegraphics[width=.24\textwidth]{stefan/nb8_iter39.png}
\includegraphics[width=.24\textwidth]{stefan/nb8_iter59.png}
\includegraphics[width=.24\textwidth]{stefan/nb8_iter79.png}
}
\subfigure{
\includegraphics[width=.24\textwidth]{stefan/nb12_iter19.png}
\includegraphics[width=.24\textwidth]{stefan/nb12_iter39.png}
\includegraphics[width=.24\textwidth]{stefan/nb12_iter59.png}
\includegraphics[width=.24\textwidth]{stefan/nb12_iter79.png}
}
\caption{Time evolution of four of the crystals obtained for the Stefan problem simulation. The snapshots represent, from left to right, iterations 96, 196, 296 and 396.} \label{fig:stefan_evolution}
\end{center}
\end{figure}

>>>>

The implementation of the Stefan problem relies on the components described in the previous sections, and it is therefore a good synthesis of the performance of the various algorithms. We monitored the performance of the code over five time iterations, as presented in Algorithm \ref{alg:stefan}, for two different maximum resolutions. In both cases, the forest is built on a $20\times20\times20$ macro-mesh. The maximum tree resolution for the small test is 9, leading to approximately 7M grid points, and the maximum resolution for the large test is 11, corresponding to 105M grid points. The level-set function is reinitialized at every time-step by applying 20 iterations of the reinitialization procedure. The results are presented in figure \ref{fig:stefan_scaling}, where ``\verb|Solution_Extension|'' refers to extrapolation procedure (see Algorithm \ref{alg:stefan} step 5). As expected from the results obtained for each component in the previous sections, our implementation of the Stefan problem exhibits very satisfactory scaling (cf.\ Table \ref{tab:scaling_stefan}).

@@

\begin{figure}[ht!]
\begin{center}
\subfigure{
\includegraphics[width=.24\textwidth]{figures/stefan_nb2_iter19.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb2_iter39.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb2_iter59.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb2_iter79.png}
}
\subfigure{
\includegraphics[width=.24\textwidth]{figures/stefan_nb5_iter19.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb5_iter39.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb5_iter59.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb5_iter79.png}
}
\subfigure{
\includegraphics[width=.24\textwidth]{figures/stefan_nb8_iter19.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb8_iter39.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb8_iter59.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb8_iter79.png}
}
\subfigure{
\includegraphics[width=.24\textwidth]{figures/stefan_nb12_iter19.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb12_iter39.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb12_iter59.png}
\includegraphics[width=.24\textwidth]{figures/stefan_nb12_iter79.png}
}
\caption{Time evolution of four of the crystals obtained for the Stefan problem simulation. The snapshots represent, from left to right, iterations 96, 196, 296 and 396.} \label{fig:stefan_evolution}
\end{center}
\end{figure}
